Behavior Driven Development in Haskell

### 2012-05-27 paper.tex
Add reasoning why type system does not always ensure correct semantics

Unfortunately, the strong type system of Haskell does not guarantee correct
semantic.

\begin{quote}
    \emph{TBD: What about dependent types and GHC's new features?}
\end{quote}

@@

    \item Motivate \verb|shouldThrow|
    \item \emph{optional:} Motivate why it's important to integrate \doctest{} with
        Cabal.
    \item \emph{optional:} Motivate \verb|hspec-discover|

>>>>

Unfortunately, the type system of Haskell does not always guarantee
correct semantics.

\begin{quote}
    TBD: Make it plausible, that the type system does not always
    guarantee correctly semantics.
    \begin{itemize}
        \item Many of the standard type classes \emph{should} adhere
            to certain laws.
        \item The type system does not enforce those laws.
        \item It is the programmers responsibility to ensure that
            instance definitions \emph{behave} as \emph{expected}.
    \end{itemize}
\end{quote}

@@

    \item \emph{optional:} Motivate why it's important to integrate \doctest{} with
        Cabal.

    \item \emph{optional:} Motivate \verb|hspec-discover|
